Relationship between solar wind, $D_{st}$, and plasmasphere trough mass density on one-hour time scales

### 2016-05-06 paper.tex
Fixing plots

\newcolumntype{L}{>{$}l<{$}} %To enable math mode in tables (for saying things like B_z)
\newcommand{\vinote}[1]{\textcolor{red}{\textbf{#1}}} %If you want \inote{#} instead of just \note #, for inline notes
\def\vnote#1\par{\textcolor{red}{\textbf{#1}}\\} %Make note bold and red, re-add newline
\newcommand{\req}{\ensuremath{\rho_{eq}}}
\newcommand{\inote}[1]{\textcolor{blue}{\textbf{#1}}} %Inline notes in blue
\def\note#1\par{\textcolor{blue}{\textbf{#1}}\\}

@@

In this work, events are defined to occur when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated by horizontal dashed lines in their respective panels of Figure~\ref{AllData}.  \vinote{need to put line in rho_eq plot.}

Figure~\ref{ccplot} shows the long-term trends of $log(\rho_{eq})$ from GOES 6 and $F_{10.7}$ computed using the median values in 27-day non-overlapping windows.  A scatter plot of these two lines is shown in the lower panel of Figure~\ref{ccplot}.  The linear correlation for GOES 6 using all measurements is found to be $0.94$, which is the same value documented by \cite{Takahashi2010} who used measurements from all satellites in the time interval of 1980 through 1991 using the constraint $0600 \leq MLT \le 1200$, $K_{p3d}\ge1.0 and $D_{st}\ge -50$~nT.  Our 27-day correlations for GOES 2, 5, and 7 are 0.81, 0.78, and 0.87, and the time range of coverage of measurements from these satellites are 1980-01-01/1983-05-16, 1983-01-01/1987-02-28, and 1983-05-27/1991-08-29 respectively.

@@

Two types of events are considered. The first is a drop in the $D_{st}$ index \vnote{Cite Kyoto} below the threshold of -50~nT. These types of events are considered in order to determine if there is a well-defined $\rho_{eq}$ dependence on geomagnetic activity/storms as indicated by $D_{st}$ index.  It is expected that the plasmasphere will exhibit two responses near these threshold crossings.  First is the movement of the plasmasphere earthward and the second is a possible increase in density due to magnetospheric processes \inote{cite}.

@@

\input{"tables/CCperltable.tex"}

@@

>>>>

\newcolumntype{L}{>{$}l<{$}} %To enable math mode in tables (for saying things like B_z)
\newcolumntype{C}{>{$}c<{$}}
\newcommand{\vinote}[1]{\textcolor{red}{\textbf{#1}}} %If you want \inote{#} instead of just \note #, for inline notes
\def\vnote#1\par{\textcolor{red}{\textbf{#1}}\\} %Make note bold and red, re-add newline
\newcommand{\req}{\ensuremath{\rho_{eq}}}
\newcommand{\inote}[1]{\textcolor{blue}{\textbf{#1}}} %Inline notes in blue
\def\note#1\par{\textcolor{blue}{\textbf{#1}}\\}

@@

In this work, events are defined to occur when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated by horizontal dashed lines in their respective panels of Figure~\ref{AllData}.  \vinote{need to put line in \req\ plot.}

Figure~\ref{ccplot} shows the long-term trends of $log(\rho_{eq})$ from GOES 6 and $F_{10.7}$ computed using the median values in 27-day non-overlapping windows.  A scatter plot of these two lines is shown in the lower panel of Figure~\ref{ccplot}.  The linear correlation for GOES 6 using all measurements is found to be $0.94$, which is the same value documented by \cite{Takahashi2010} who used measurements from all satellites in the time interval of 1980 through 1991 using the constraint $0600 \leq MLT \le 1200$, $K_{p3d}\ge1.0$ and $D_{st}\ge -50$~nT.  Our 27-day correlations for GOES 2, 5, and 7 are 0.81, 0.78, and 0.87, and the time range of coverage of measurements from these satellites are 1980-01-01/1983-05-16, 1983-01-01/1987-02-28, and 1983-05-27/1991-08-29 respectively.

@@

Two types of events are considered. The first is a drop in the $D_{st}$ index \vinote{Cite Kyoto} below the threshold of -50~nT. These types of events are considered in order to determine if there is a well-defined $\rho_{eq}$ dependence on geomagnetic activity/storms as indicated by $D_{st}$ index.  It is expected that the plasmasphere will exhibit two responses near these threshold crossings.  First is the movement of the plasmasphere earthward and the second is a possible increase in density due to magnetospheric processes \inote{cite}.

@@

@@

\newpage
\input{"tables/CCperltable.tex"}
